Revisiting~the~Classics: Online~RL~in~the~Programmable~Dataplane

### 2021-05-31 paper/paper.tex
Some minor changes to stats extraction.

\usepackage{etoolbox}
\usepackage[binary-units, per-mode=symbol]{siunitx}
\robustify\bfseries
\robustify\emph
%\robustify\uline
\sisetup{detect-all, range-phrase=--, range-units=single, detect-weight=true,detect-inline-weight=math, table-format=1.3}

@@

\fakepara{Co-existence with the dataplane}
No packet loss incurred
?? mention actually achieved rates?

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.45\linewidth}
		\resizebox{1.0\linewidth}{!}{
%			\includegraphics{../plots/build/stress/heat-latency-median}
			\includegraphics{../plots/build/stress/heat-latency-two-9}
		}
		\caption{Ayy?}
	\end{subfigure}
	\hspace{0.05\linewidth}
		\begin{subfigure}{0.45\linewidth}
		\resizebox{1.0\linewidth}{!}{
			\includegraphics{../plots/build/stress/histo-1518B-0-10}
		}
		\caption{Ayy?}
	\end{subfigure}
	\caption{Ayy.}
\end{figure}

>>>>

\usepackage{etoolbox}
\usepackage[binary-units, per-mode=symbol]{siunitx}
\robustify\bfseries
\robustify\emph
%\robustify\uline
\sisetup{detect-all, range-phrase=--, range-units=single, detect-weight=true,detect-inline-weight=math, table-format=1.3}
\DeclareSIUnit{\packet}{p}

@@

\fakepara{Co-existence with the dataplane}
We were able to saturate the \SI{40}{\giga\bit\per\second} link for packet sizes above \SI{256}{\byte}.
For frame sizes of \SIlist{64;128;256}{\byte} input traffic rates were \SIlist{17.4;32.9;37.0}{\giga\bit\per\second} respectively (\SIlist[per-symbol=p,sticky-per=true]{33.9;32.2;18.1}{\mega\packet\per\second}).
Passing traffic over the loaded NFP device running \approachshort, no packet losses were incurred at any rate of RL actions.

We show the effect of RL workloads on the round-trip latencies of cross traffic through \cref{fig:dataplane-coop}.
As observed latency measures do not obey a normal distribution, we employ a one-tailed \emph{Mann-Whitney U test} to mark statistically significant population increases in latency ($p < 0.05$) with a "+".
In general, we observe that statistically significant latency increases concentrate around smaller packet sizes.
All (bar one) of these affected \nth{99} percentile latencies by under \SI{0.38}{\percent} (at most \SI{78}{\nano\second}).

Is this anomaly just burstiness? It's \SI{222}{\nano\second} (1.175 percent)

?? Cross-island/chip traffic must cross command push pull bus.

\cref{fig:dataplane-example} shows one such example...

@@

\cref{fig:dataplane-coop}

?? Odd two-tailed behaviour on 1518B

?? Why spike in significance at 256? Likely due to packet segmentation in NFP (i.e., split between memory regions with body in EMEM).

\begin{figure}
	\centering
	\begin{subfigure}{0.45\linewidth}
		\resizebox{1.0\linewidth}{!}{
%			\includegraphics{../plots/build/stress/heat-latency-median}
			\includegraphics{../plots/build/stress/heat-latency-two-9-rel}
%			\includegraphics{../plots/build/stress/heat-latency-two-9-perc}
		}
		\caption{Deviations in \nth{99} percentile cross-traffic latencies.\label{fig:dataplane-heat}}
	\end{subfigure}
	\hspace{0.05\linewidth}
		\begin{subfigure}{0.45\linewidth}
		\resizebox{1.0\linewidth}{!}{
			\includegraphics{../plots/build/stress/histo-128B-0-3}
		}
		\caption{Distribution of round-trip latencies for \SI{128}{\byte} packets.\label{fig:dataplane-example}}
	\end{subfigure}
	\caption{At most \SI{1.5}{\percent}... "+" symbols denote statistically significant ($p < 0.05$) increases in population latency, concentrated on smaller packet sizes.\label{fig:dataplane-coop}}
\end{figure}
